---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FinalProj561

<!-- badges: start -->
<!-- badges: end -->

The goal of FinalProj561 is to generate several samples contains values follow a normal
distribution. Then made statistical summary by number and graphs.

PkgDown URL: https://chenyihan1999.github.io/FinalProj561/

GitHub URL: https://github.com/CHENYIHAN1999/FinalProj561

## Installation

You can install the development version of FinalProj561 like so:

``` {r}
devtools::install_github("CHENYIHAN1999/FinalProj561")
```

Upon completion, you can run the following code (in R):
```{r}
library(FinalProj561)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(FinalProj561)

result <- generate_samples(5, 10, 70, 3.3)
mean_result <- calculate_means_and_plot(result)
samples_result <- result$samples
count_result <- count_values_and_plot_histogram(samples_result, 50, "smaller")
```

# Session info

This package was developed in the following environment
```{r}
devtools::session_info()
```












